{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-15 bmvc_review.tex
Table Updated

\documentclass{bmvc2k}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
% \usepackage{algorithm}		% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

In this paper, we propose a single-target tracking algorithm, with no
offline training, aiming at running on any embedded or mobile
platforms. Specifically, we would like to make our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300-400$ fps so that it could run, at least,
faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would be very hard to compare an Intel
  or AMD processor running on a desktop or a laptop with that, e.g.,
  ARM, of a single-board, embedded system in terms of run-time
  performance of a computer vision algorithm. This is primarily due to
  the difference in their architectures. To derive this number, we
  assume that there is roughly, at least, an 1/10th scale down of
  computational resources from a typical PC to an embedded system. We
  found such a scale-down in computation based on exemplar processors,
  e.g., Intel's i7 quad-core vs ARMv8 dual-core.}

@@

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results (yellow rectangles) by the
  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
  is challenging for object tracking as a target's scale is changed
  drastically in a few frames.}
\label{ResultsIntroduction}
\end{figure*}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We
aims at developing an object tracking algorithm that ``efficiently''
runs on an embedded system, a drone, for example, in ``high speed,''
$\ge 300$ fps. Given this, we believe that the UAV123 data is a good
fit in evaluating the performance of the proposed algorithm. In
addition, in the UAV123 data, there are many challenging, realistic
scenes, e.g., abrupt scale/illumination changes. Although we are
primarily interested in developing an algorithm for mobile, embedded
robotic applications, it is also important to compare the performance
of the proposed algorithm with those of the state-of-the-art in a
nominal dataset for comparison. To this end, we chose the OTB100 data
that contains the videos recorded from smart phones and typical
cameras in perspective view. Lastly, we tested the proposed algorithm
on a temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to see from this
experiment is to evaluate how robust the proposed algorithm is to
drastic motions of camera and targets.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing specific challenges in single,
target tracking problem. Thus each of them should have different
values for the optimal parameters. For instance, the primary task of
the translation filter, $R_{t}^{L}$ is to estimate the translation of
a target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.6$, $0.4$, and
$0.4$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate
as $0.12$ for $R_{t}^{L}$. For our particle filter implementation, we
empirically set the number of particles to $1000$ to balance the
run-time performance and accuracy. To keep the level of variance among
the particles reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

@@

\textbf{Performance on UAV123 Dataset} We compared the performance of
the proposed algorithm with those of the state-of-the-art high speed
tracking algorithms by the \textit{Precision} and
\textit{Success\:Rate} metrics. For the precision, we rank the
trackers based on the precision numbers at 20 pixels whereas in the
success rate plots, trackers are ranked based on area under curve
(AUC) scores. The tracking algorithms used for the comparison include
ones in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high},
CSK \cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50), i.e., SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels precision
metric. Three algorithms, SAMF, DSST, and Struck did about 5\% better
than ours in accuracy, but 10-20\% slower than ours. For the scale
adaptation, {\it E}nKCF did second best in terms of \textit{area under
  curve} (AUC) value for the success rate plot. It outperformed other
tracking methods in high-speed by about $20\%$-$25\%$ in AUC
metric. In addition, it performed even better than those algorithms
that are slow, but a bit better in precision. For example, for AUC,
{\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while
running at more than $10$ and $30$ times faster.

We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
tracker ({\it m}LCT) and run $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given order. $R_{t}^{S}$ uses the translation estimation given by $R_{t}^{L}$ to update
translation and $R_{s}$ uses the final translation estimation given by $R_{t}^{S}$ to update scale. Interestingly, running two complementary translation filter results in significant improvement
at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT  ($R_{t}^{L}$+$R_{s}$) & LCT  ($R_{t}^{S}$+$R_{s}$) & {\it m}LCT  ($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
\hline\hline
Pr. ($20$px) & 53.9 & 48.09 & 52.50 & \color{red} 55.85 & 52.14 & \textbf{58.16} \\
SR ($50\%$) & \color{red} 40.2 & 36.04 & 37.85 & 39.89 & 38.51 & \textbf{41.58} \\
FPS & \color{red} 416 & 370 & \textbf{425}  & 135 & 151 & 99 \\
\hline
\end{tabular}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. The 2nd method removes $R_{t}^{S}$ (fig.~\ref{Workflows}) and replaces with $R_{t}^{L}$ whereas the 3th one removes $R_{t}^{L}$. We decouple the re-detection module of the LCT tracker and particle filter from all the methods as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF. The KCFs highlighted in LCT are applied in every frame in the listed order as proposed in
\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison. In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\leq50$fps).} 
\label{table:Comparison_to_LCT}
\end{table}

@@

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
shows the results on the OTB100 dataset. Same as with UAV123 dataset,
we observed a similar performance. In particular, {\it E}nKCF showed a
good performance for handling the scale changes. It was the third best
and the second fastest tracking algorithm. For the precision metric,
{\it E}nKCF performed slightly better than most of tracking algorithms
in high-speed trackers. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_UAV123.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_UAV123.eps}}
\bmvaHangBox{\includegraphics[width=2.80cm]{./figures/Precision_OTB100.eps}}
\bmvaHangBox{\includegraphics[width=3.20cm]{./figures/Success_OTB100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with those of the
  state-of-the-art tracking algorithms on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}
%\begin{figure}[!h]
%\centering
%\begin{tabular}{ccc}
%\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_OTB100.eps}}
%\bmvaHangBox{\includegraphics[width=3.80cm]{./figures/Success_OTB100.eps}}\\
%\end{tabular}
%\caption{Comparison of {\it E}nKCF's performance with those of the
%  state-of-the-art tracking algorithms on the OTB100 dataset.}
%\label{fig:OTB100_DATASET}
%\end{figure}

>>>>

\documentclass{bmvc2k}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

In this paper, we propose a single-target tracking algorithm, with no
offline training, aiming at running on any embedded or mobile
platforms. Specifically, we would like to make our algorithm 1) learn
the appearance model of a target on the fly and 2) run as fast on a
typical desktop as up to $300-450$ fps so that it could run, at least,
faster than 30 fps when it is deployed on a low-end, embedded
system.\footnote{In general, it would be very hard to compare an Intel
  or AMD processor running on a desktop or a laptop with that, e.g.,
  ARM, of a single-board, embedded system in terms of run-time
  performance of a computer vision algorithm. This is primarily due to
  the difference in their architectures. To derive this number, we
  assume that there is roughly, at least, an 1/10th scale down of
  computational resources from a typical PC to an embedded system. We
  found such a scale-down in computation based on exemplar processors,
  e.g., Intel's i7 quad-core vs ARMv8 dual-core.}

@@

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Examples of tracking results (yellow rectangles) by the
  proposed method on the ``UAV123'' dataset. This ``UAV123'' dataset
  is challenging for object tracking as a target's scale is changed
  drastically in a few frames.}
\label{ResultsIntroduction}
\end{figure*}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To evaluate the performance of the proposed algorithm, we choose two
publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footages of 123 objects. We
aim at developing an object tracking algorithm that ``efficiently''
runs on an embedded system, a drone, for example, in ``high speed,''
$\ge 300$ fps. Given this, we believe that the UAV123 data is a good
fit in evaluating the performance of the proposed algorithm. In
addition, in the UAV123 data, there are many challenging, realistic
scenes, e.g., abrupt scale/illumination changes. Although we are
primarily interested in developing an algorithm for mobile, embedded
robotic applications, it is also important to compare the performance
of the proposed algorithm with those of the state-of-the-art in a
nominal dataset for comparison. To this end, we chose the OTB100 data
that contains the videos recorded from smart phones and typical
cameras in perspective view. Lastly, we tested the proposed algorithm
on a temporally down-sampled version of the UAV123 dataset, called
UAV123$\_$10fps dataset. What we would like to see from this
experiment is to evaluate how robust the proposed algorithm is to
drastic motions of camera and targets.

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing specific challenges in single,
target tracking problem. Thus each of them should have different
values for the optimal parameters. For instance, the primary task of
the translation filter, $R_{t}^{L}$ is to estimate the translation of
a target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale filter update
threshold, $T_{R_{s}}$, to 4. For our particle filter implementation, we
empirically set the number of particles to $1000$ to balance the
run-time performance and accuracy. To keep the level of variance among
the particles reasonable, we performed the re-sampling only when the
\textit{efficient number of samples} ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $) is lower than a pre-defined
threshold.

@@

\textbf{Performance on UAV123 Dataset} We compared the performance of
the proposed algorithm with those of the state-of-the-art high speed
tracking algorithms by the \textit{Precision} and \textit{Success\:Rate} metrics. 
For the precision, we rank the trackers based on the precision numbers at 20 pixels 
whereas in the success rate plots, trackers are ranked based on area under curve
(AUC) scores. The tracking algorithms used for the comparison include
ones in high-speed ($\geq$300 fps), i.e., KCF\cite{henriques2015high},
CSK \cite{henriques2012exploiting}, DCF\cite{henriques2015high}, and
MOSSE\cite{bolme2010visual,henriques2015high} and ones in relatively
lower-speed ($\geq$50), i.e., SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, Struck\cite{hare2012efficient},
MUSTER \cite{hong2015multi}. TLD \cite{kalal2012tracking}, and OAB
\cite{zhang2012robust}. Figure \ref{fig:UAV123_DATASET} shows the
results on the UAV123 dataset. {\it E}nKCF outperformed most of the
high-speed tracking methods by $3\%$-$15\%$ at 20 pixels precision
metric. Three algorithms, SAMF, DSST, and Struck did about 5\% better
than ours in accuracy, but 10-20 times slower than ours. For the scale
adaptation, {\it E}nKCF did second best in terms of \textit{area under
  curve} (AUC) value for the success rate plot. It outperformed other
tracking methods in high-speed by about $20\%$-$25\%$ in AUC
metric. In addition, it performed even better than those algorithms
that are slow, but a bit better in precision. For example, for AUC,
{\it E}nKCF outperformed Struck and DSST by $5\%$ and $10\%$ while
running at more than $10$ and $30$ times faster.
\begin{figure}[!h]
\raggedright
\begin{tabular}{ccc}
\tiny \textbf{UAV123}\hspace{.45\linewidth}\textbf{OTB100}\\
\bmvaHangBox{\includegraphics[width=2.90cm]{./figures/Precision_UAV123.eps}}
\bmvaHangBox{\includegraphics[width=3.35cm]{./figures/Success_UAV123.eps}}
\bmvaHangBox{\includegraphics[width=2.90cm]{./figures/Precision_OTB100.eps}}
\bmvaHangBox{\includegraphics[width=3.35cm]{./figures/Success_OTB100.eps}}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's performance with other trackers on the UAV123 and OTB100 datasets.}
\label{fig:UAV123_DATASET}
\end{figure}

We also compare the proposed {\it E}nKCF tracker to the LCT \cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}. 
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$,  $R_{s}$) in  {\it E}nKCF, we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ with similar
run-time performance. On the other hand, we employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as we run filters in every frame. Running another filter, 
$R_{t}^{L}$ or $R_{t}^{S}$, in the {\it E}nKCF framework not only gives us significantly higher run-time performance but also higher accuracy. Finally, we modify the LCT
tracker ({\it m}LCT) and run $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given order. $R_{t}^{S}$ uses the translation estimation given by $R_{t}^{L}$ to update
translation and $R_{s}$ uses the final translation estimation given by $R_{t}^{S}$ to update scale. Interestingly, running two complementary translation filter results in significant improvement
at the cost of decreased run-time performance. In conclusion, running two complementary translation filter and a scale filter in the {\it E}nKCF framework not only provides
high speed but also more accurate tracker than the baseline methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & LCT($R_{t}^{L}$+$R_{s}$) & LCT($R_{t}^{S}$+$R_{s}$) & {\it m}LCT($R_{t}^{L}+R_{t}^{S}$+$R_{s}$) \\
\hline\hline
Pr. ($20$px) & 53.9 & 48.93 &52.41 & 48.10 & \color{red} 55.85 & 52.14 & \textbf{58.16} \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 39.89 & 38.51 & \textbf{41.58} \\
FPS & \color{red} 416 & 412 & 370 & \textbf{425}  & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed KCFs in UAV123 dataset. The 2nd method swaps the order of $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The 3th method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the 3th one removes $R_{t}^{L}$. We decouple the re-detection module of the LCT tracker and particle filter from all the methods as we focus on the comparison of the multiple correlation filter framework between LCT and  {\it E}nKCF. The KCFs highlighted in LCT are applied in every frame in the listed order as proposed in
\cite{ma2015long}, however, only three scale candidates ($1.02$, $1.00$, $1.00/1.02$) are used in $R_{s}$ for fair comparison. In the original paper, 33 scales with scale factor 1.02 is considered, resulting in low fps ($\approx30$fps).} 
\label{table:Comparison_to_LCT}
\end{table}

@@

\textbf{Performance on OTB100 Dataset} Figure \ref{fig:UAV123_DATASET}
shows the results on the OTB100 dataset. Same as with UAV123 dataset,
we observed a similar performance. In particular, {\it E}nKCF showed a
good performance for handling the scale changes. It was the third best
and the second fastest tracking algorithm. For the precision metric,
{\it E}nKCF performed slightly better than most of tracking algorithms
in high-speed trackers. Interestingly, it outperformed another
correlation filter based tracker, DSST, but performing $5\%$ behind of
another low-speed scale adaptive SAMF tracker.
%\begin{figure}[!h]
%\centering
%\begin{tabular}{ccc}
%\bmvaHangBox{\includegraphics[width=3.30cm]{./figures/Precision_OTB100.eps}}
%\bmvaHangBox{\includegraphics[width=3.80cm]{./figures/Success_OTB100.eps}}\\
%\end{tabular}
%\caption{Comparison of {\it E}nKCF's performance with those of the
%  state-of-the-art tracking algorithms on the OTB100 dataset.}
%\label{fig:OTB100_DATASET}
%\end{figure}
